AI-Based Detection of Jamming Attacks In 6G Drone Networks

### 2024-09-26 article.tex
Finished the abstract

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{}

>>>>

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{Drones are integral to various industries and their future integration with 6G network will significantly enhance their capabilities, enabling a wide range of new applications based on autonomous operation. However, drone networks are particularly vulnerable to Jamming attacks, a type of Availability attack that can disrupt network operation and hinder drone functionality. In this paper, we propose an unsupervised machine learning approach for the detection of constant and periodic jamming attacks, using the Isolation Forest algorithm. The base model was tuned to best fit the proposed scenario, but faced challenges related to environmental noise in the dataset. To address this, we introduced a Majority Rule module that significantly reduced the number of false positives, while still achieving high accuracy and precision. Our approach outperforms the standard Isolation Forest model in the detection of both constant and periodic jamming attacks, while reducing the occurrence of false positives in normal traffic. Finally, we discuss the potential integration of the proposed solution in 6G-enabled drone networks, as a lightweight solution for improved security against jamming attacks. }
